Endogenous Politics and \\ the Design of Trade Institutions

### 2017-01-18 draft.tex
add references to my previous work per AEJ:micro guidance

\begin{document}
\title{Endogenous Politics and the Design of Trade Institutions\thanks{I thank Kyle Bagwell, Mostafa Beshkar, Rick Bond, Renee Bowen, Chad Bown, Paola Conconi, David DeRemer, James Lake, Nuno Limao, Giovanni Maggi, Devashish Mitra, Peter Rosendorff, Bob Staiger, Maurizio Zanardi, Ben Zissimos and participants in seminars at McGill, Rochester, Ryerson, Wesleyan, ETSG, InsTED, the Midwest International Trade Meetings, PEIO and SITE for very helpful comments and discussions.}}
\author{Kristy Buzard\thanks{Syracuse University, Economics Department. Email: kbuzard@syr.edu. http://faculty.maxwell.syr.edu/kbuzard.}}
\date{\vskip-.1in \today}
\maketitle

@@

\subsection{Setup}
\label{sec:economic}
I begin by describing the economic setting within which trade occurs.\footnote{Note this is the economic environment of \Textcite{gh95} specialized to two tradable goods with symmetry assumed for simplicity of exposition.} It is a three-good model with two countries: home (no asterisk) and foreign (asterisk). In the home country, the representative consumer maximizes
\[
  u = c_N + u_X(c_X) + u_Y(c_Y).
\]
where $c_i$ for $i \in \left\{i,X,Y\right\}$ denotes consumption of the numeraire, X and Y goods respectively. The functions $u_X(\cdot)$ and $u_Y(\cdot)$ are assumed to be increasing, strictly concave and differentiable. The demand functions for $X$ and $Y$ are written $D(P_i)$ where $D(\cdot)$ is the inverse of $u'_i(\cdot)$ and $P_i$ ($P_i^*$) denotes the home (foreign) price of good $i \in \left\{N,X,Y\right\}$. Demand is assumed symmetric in foreign.

>>>>

\begin{document}
\title{Endogenous Politics and the Design of Trade Institutions\thanks{I thank Kyle Bagwell, Mostafa Beshkar, Rick Bond, Renee Bowen, Chad Bown, Paola Conconi, David DeRemer, James Lake, Nuno Lim\~ao, Giovanni Maggi, Devashish Mitra, Peter Rosendorff, Bob Staiger, Maurizio Zanardi, Ben Zissimos and participants in seminars at McGill, Rochester, Ryerson, Wesleyan, ETSG, InsTED, the Midwest International Trade Meetings, PEIO and SITE for very helpful comments and discussions.}}
\author{Kristy Buzard\thanks{Syracuse University, Economics Department. Email: kbuzard@syr.edu. http://faculty.maxwell.syr.edu/kbuzard.}}
\date{\vskip-.1in \today}
\maketitle

@@

\subsection{Setup}
\label{sec:economic}
I begin by describing the economic setting within which trade occurs.\footnote{Note this is the economic environment of \Textcite{gh95} specialized to two tradable goods with symmetry assumed for simplicity of exposition. The basic economic and political structure is similar in many ways to that in \Textcite{buzard2013b}.} It is a three-good model with two countries: home (no asterisk) and foreign (asterisk). In the home country, the representative consumer maximizes
\[
  u = c_N + u_X(c_X) + u_Y(c_Y).
\]
where $c_i$ for $i \in \left\{i,X,Y\right\}$ denotes consumption of the numeraire, X and Y goods respectively. The functions $u_X(\cdot)$ and $u_Y(\cdot)$ are assumed to be increasing, strictly concave and differentiable. The demand functions for $X$ and $Y$ are written $D(P_i)$ where $D(\cdot)$ is the inverse of $u'_i(\cdot)$ and $P_i$ ($P_i^*$) denotes the home (foreign) price of good $i \in \left\{N,X,Y\right\}$. Demand is assumed symmetric in foreign.

### 2017-01-18 intro.tex
add references to my previous work per AEJ:micro guidance

We miss important dynamics like this one when we assume political pressure is exogenous as is done for tractability in almost all the literature that studies trading rules and institutions (see \Textcite{mrc2007} and \Textcite{lt} for notable exceptions). The main contribution of this paper is to provide a tractable framework for integrating lobbying incentives into these analyses. This framework can be used to study a wide range of questions, including dispute settlement design, optimal retaliation schemes and depth of integration among others. It's well-positioned to examine the interactions between exogenous shocks and lobbying incentives and will be useful for shedding light on questions surrounding how governments choose among protective measures over time.

>>>>

We miss important dynamics like this one when we assume political pressure is exogenous as is done for tractability in almost all the literature that studies trading rules and institutions (see \Textcite{mrc2007}, \Textcite{lt} and \Textcite{buzard2013a} for exceptions). The main contribution of this paper is to provide a tractable framework for integrating lobbying incentives into these analyses. This framework can be used to study a wide range of questions, including dispute settlement design, optimal retaliation schemes and depth of integration among others. It's well-positioned to examine the interactions between exogenous shocks and lobbying incentives and will be useful for shedding light on questions surrounding how governments choose among protective measures over time.
